Adopting agile in the large: motivations, success factors and challenges

### 2014-04-21 journal/article.tex
Reasons to change

>>>>

As stated by research question 1 we investigated the reasons why organizations
start a transformation process towards agile software development. Most primary
studies gave reasons for starting the transformation, and only 7 cases of 42 did
not mention any reasons. In cases giving no specific reason to change it was
mentioned simply that the management had decided to change the organization.

Some cases reported that the organization had been successful in waterfall
delivery for a long time before the agile transformation.
